\chapter{Future Scope}

\begin{itemize}

\item \textbf{Distributed Training Infrastructure:}

The platform can be enhanced with a distributed training system that allows users to leverage multiple servers and hardware resources such as CPUs and GPUs without requiring in-depth knowledge of cloud technologies. Users can simply select their preferred compute option (CPU/GPU) from an intuitive dropdown interface, and the system will automatically allocate resources and manage the training process across distributed nodes. This approach eliminates the complexity of cloud setup, optimizes training performance for large datasets and deep learning models, and makes scalable machine learning accessible to all users.\\

\item \textbf{Continuous Model Retraining:}

To ensure that deployed models remain accurate and relevant over time, the platform will incorporate automated retraining mechanisms. This feature will monitor incoming data for distribution shifts or model performance degradation and trigger retraining workflows when necessary. By enabling continuous learning, InferX ML will support real-world production scenarios where data evolves dynamically, ensuring that predictions remain reliable without manual intervention. \\

\item \textbf{Enhanced Model Explainability:}

Future improvements will focus on advancing model interpretability by integrating multiple explainability techniques such as SHAP and LIME. These tools will provide deeper insights into feature importance, local and global explanations, and decision boundaries of models. Enhanced visualization dashboards and user-friendly explanation reports will help users better understand how models make predictions, thereby increasing trust, transparency, and adoption of AI solutions. \\

\item \textbf{Cloud Deployment and API Integration:}

InferX ML will be extended to support seamless cloud deployment and API-based access to trained models. Users will be able to deploy models on cloud platforms and generate REST APIs for real-time inference, enabling easy integration with external applications, websites, and enterprise systems. \\

\end{itemize}